---
title: "HRMIS Analytics"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

This article shows examples for how to analyze harmonized human resource management information system (HRMIS) data, organized into three main modules: Organization, Worker, and Contract. The contents of each module are described in `vignette("standard_dictionary")`

# A demo data

Suppose the Government of Brazil shared with us an extraction of their HRMIS data. First, let's take a closer look at the data.

```{r}
library(govhr)
library(dplyr)
library(ggplot2)
```


```{r, include = FALSE}
library(stringr)
library(polyglotr)

bra_hrmis_contract <- bra_hrmis |>
  mutate(
    occupation_native  = str_to_lower(CARREIRA),
    occupation_english = str_to_lower(
      google_translate(
        text = CARREIRA,
        source_language = "pt",
        target_language = "en"
      )
    )
  ) |>
  transmute(
    contract_id = MATRICULA,
    worker_id = CPF,
    org_id = paste(ORGAO, COD_ORGAO, ANO_PAGAMENTO, sep = "-"),
    ref_date = as.Date(paste(ANO_PAGAMENTO, MES_REFERENCIA, "01", sep = "-")),
    base_salary_lcu = SALARIO_BASE,
    allowance_lcu = ABONO_PERMANENCIA,
    gross_salary_lcu = SALARIO_BRUTO,
    net_salary_lcu = SALARIO_LIQUIDO,
    whours = as.numeric(JORNADA),
    country_code = "BRA",
    country_name = "Brazil",
    adm1_name = "Alagoas",
    adm1_code = "AL",
    start_date = as.Date(as.integer(DATA_ADMISSAO), origin = "1899-12-30"),
    end_date = NA,
    paygrade = CLASSE,
    seniority = NIVEL,
    occupation_native = occupation_native,
    occupation_english = occupation_english,
    occupation_iscocode = occupation_iscocode,
    occupation_isconame = occupation_isconame,
    contract_type_native = TIPO_CONTRATO,
    contract_type_code = case_when(
      TIPO_CONTRATO %in% c("EFETIVO", "EFETIVO COMISSIONADO") ~ "perm",
      TIPO_CONTRATO == "EXCLUSIVAMENTE COMISSIONADO" ~ "fixed_term",
      TIPO_CONTRATO %in% c("TEMPORÁRIO", "TEMPOR¡RIO") ~ "temp",
      is.na(TIPO_CONTRATO) ~ NA_character_,
      TRUE ~ "other"
    )
  )
```

